Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-05-18 Chapter-6/6-PionCrossSection.tex
s

\chapter{Negative Pion Cross Section Measurement}\label{ch:PionXS}
%{\raggedleft ``\emph{Y ella es flama que se eleva, Y es un p\'ajaro a volar} \par}
%{\raggedleft \emph{En la noche que se incendia, Estrella de oscuridad}"\par}
%{\raggedleft \emph{Que busca entre la tiniebla, La dulce hoguera del beso}"\par}
%{\raggedleft -- Lila Downs, Benediction And Dream,  -- \par}

@@

\begin{figure}[p]
\centering  
\includegraphics[width=0.48\textwidth]{Chapter-4/Images/face-smile-big.png}
\includegraphics[width=0.48\textwidth]{Chapter-4/Images/face-smile-big.png}
\caption{Raw number of interacting pion candidates as a function of the reconstructed kinetic energy for the 60A runs (lef) and for the 100A runs (right). The statistical uncertainties are shown in azure, the systematic uncertainties in blue.}
\label{fig:InteractingRaw}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.48\textwidth]{Chapter-4/Images/face-smile-big.png}
\includegraphics[width=0.48\textwidth]{Chapter-4/Images/face-smile-big.png}
\caption{Raw number of incident pion candidates as a function of the reconstructed kinetic energy for the 60A runs (lef) and for the 100A runs (right). The statistical uncertainties are shown in azure, the systematic uncertainties in blue.}
\label{fig:IncidentRaw}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.48\textwidth]{Chapter-4/Images/face-smile-big.png}
\includegraphics[width=0.48\textwidth]{Chapter-4/Images/face-smile-big.png}
\caption{Raw ($\pi^-$-Ar) total hadronic cross section for the 60A runs (lef) and for the 100A runs (right). The statistical uncertainties are shown in azure, the systematic uncertainties in blue.}
\label{fig:XSRaw}
\end{figure}

>>>>

\chapter{Negative Pion Cross Section Measurement}\label{ch:PionXS}
%{\raggedleft ``\emph{Y ella es flama que se eleva, Y es un p\'ajaro a volar} \par}
%{\raggedleft \emph{En la noche que se incendia, Estrella de oscuridad}"\par}
%{\raggedleft \emph{Que busca entre la tiniebla, La dulce hoguera del beso}"\par}
%{\raggedleft -- Lila Downs, Benediction And Dream,  2002-- \par}

@@

\begin{figure}[p]
\centering  
\includegraphics[width=0.48\textwidth]{Chapter-6/Images/Plots60A_StatSyst.png}
\includegraphics[width=0.48\textwidth]{Chapter-6/Images/Plots100A_StatSyst.png}
\caption{Raw number of interacting pion candidates as a function of the reconstructed kinetic energy for the 60A runs (lef) and for the 100A runs (right). The statistical uncertainties are shown in azure, the systematic uncertainties in blue.}
\label{fig:InteractingRaw}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.48\textwidth]{Chapter-6/Images/Plots60A_StatSysc.png}
\includegraphics[width=0.48\textwidth]{Chapter-6/Images/Plots100A_StatSysc.png}
\caption{Raw number of incident pion candidates as a function of the reconstructed kinetic energy for the 60A runs (lef) and for the 100A runs (right). The statistical uncertainties are shown in azure, the systematic uncertainties in blue.}
\label{fig:IncidentRaw}
\end{figure}

\begin{figure}
\centering  
\includegraphics[width=0.48\textwidth]{Chapter-6/Images/Plots60A.png}
\includegraphics[width=0.48\textwidth]{Chapter-6/Images/Plots100A.png}
\caption{Raw ($\pi^-$-Ar) total hadronic cross section for the 60A runs (lef) and for the 100A runs (right). The statistical uncertainties are shown in azure, the systematic uncertainties in blue.}
\label{fig:XSRaw}
\end{figure}
